---
title: "Day1_Notes"
author: "Elli"
date: "15 3 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Notes during Lecture

<https://docs.google.com/document/d/1XMRyRu4VAb1kXgstZc61qrt0gKggWX5A5OYXpGZI2P8/edit>

Document to ask questions

brakets around x<-4 will automatically print it

```{r}

(x<-4)

```

round brakets only for functions

which(age>=18) gives us vector of indices, but if age[which(age>=18)] or age[age>=18] we get values that are >=18.

Factor sets the levels to distinct values/characters/possibilities. NEVER convert factor directly into a numeric --> have to do 2 steps!
1st transform into character, then to numeric. R saves factors under diffferent class called "factor".



# Exercises
## 1.1
```{r}
sqrt(144)
log2(24)
2/3*(sqrt(9)-log10(1000))^2+5/6

```
##1.2
```{r}
x <- 2
y <- 10
y!=x
y==x
y>=x
(z <- y/x)
y/2

```

Environment shows variables defined by me.

## 1.3
not possible due to number at the beginning of the variable. Change number.

## 1.4
```{r}
Name <- "Maria"
Age <- 30
PhD <- TRUE
class(Name)
class(Age)
class(PhD)
is.na((PhD))

```

## 1.5
```{r}
x <- -5
y <- 0
z <- x / y
z

```

## 1.6
```{r}
b <- 16
h <- 9
(A <- b*h)
A > 100

```

## 1.7
```{r}
num <- c(seq(1,10,1))
alpha <- letters[1:5]
mix <- c(num, alpha)
class(mix)


```

## 1.8
```{r}
expDesign <- factor(c(rep("Wildtype", 3), rep("Mutant", 4)))
class(expDesign)
length(expDesign)
levels(expDesign)
names(expDesign) <- c( paste0("M", seq(1, 7, 1)))
expDesign
```

## 1.9
no differences in Value, class or length.

## 1.10
```{r}
x <- c(0, -1, 3, 10, -14, 7.5, 9)
y <- x[c(1,3,4,6,7)]

y1 <- x[c(-2, -5)]
y2 <- x[c(T, F, T, T, F, T, T)]
y3 <- x[x >0]

```

## 1.11
```{r}
normExpr <- c(10.2, 11.4, 4.0)
names(normExpr) <- c("CD8A", "CD8B", "PDCD1")

normExpr[1:2]
normExpr[c(1,2)]
normExpr[c("CD8A", "CD8B")]

```

## 1.12
```{r}
cellFractions <- c(-0.1, 0.4, -0.4, 0.5, 0.2)
cellFractions[cellFractions<=0] <- 0

```