---
title: "Day2_Notes"
author: "Elli"
date: "16 3 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Notes during Lecture

<https://docs.google.com/document/d/1XMRyRu4VAb1kXgstZc61qrt0gKggWX5A5OYXpGZI2P8/edit>

Document to ask questions

.. means going out of current directory
. means in the current directory

difference between list.files("") for directories from working directory
and ls() which shows environment

use source to load R script

save RData with save(x, y, file = "....")

load RData with load()

setdiff() only looks for elements from 1st vector in 2nd vector!

# Exercises
## 2.1
```{r}
dir.create("./Rcourse_day2")
dir.create("./Rcourse_day2/Data")
dir.create("./Rcourse_day2/Scripts")
setwd("./Rcourse_day2/Scripts")
getwd()


```
##2.2
```{r}
b <- 5
h <- 4
save(b, h, file = "./Rcourse_day2/Data/triangle.RData")


```


## 2.4
```{r}
rm(list=ls())
load("./Rcourse_day2/Data/triangle.RData")
source("./Rcourse_day2/Scripts/Triangle_area.R")
A <- getArea(b,h)



```

## 2.5
```{r}
x <- c(1, 2, 200, 6, 80, 23)
y <- c(100, 50, 5, 30, 1, 20)
mean(x)
mean(y)
var(x)
var(y)
cor(x, y, method="spearman")

```

##2.6
```{r}
mLen <- c(31, 28, 31, 30,
31, 30, 31, 31,
30, 31, 30, 31)
names(mLen) <- c("Jan", "Feb", "Mar", "Apr",
"May", "Jun", "Jul", "Aug",
"Sep", "Oct", "Nov", "Dec")
table(mLen)

```

##2.7
```{r}
x <- sample(1:90, 10)
y <- sort(x)

```

##2.8
```{r}
x <- seq(1, 5)
y <- seq(3, 7)
a <- intersect(x,y)
b <- setdiff(y,x)

```

##2.9
```{r}
x <- c(2, 4, 5, 7, 8)
y <- c(2, 4, 6, 8, 10)
z <- c(2, 3, 4, 5, 6)
a <- intersect(intersect(x,y),z)
b <- setdiff(intersect(x,y),z)

```

## 2.10
```{r}
firstNsum <- function(n) {
a <- seq(1,n)
return(sum(a))
}

firstNsum2 <- function(n) {
n*(n+1)/2
}
firstNsum(10)
firstNsum2(10)
firstNsum(20)
firstNsum2(20)
firstNsum(100)
firstNsum2(100)

```

## 2.11
```{r}
FtoCtemp <- function(F){
C <- 5/9*(F-32)
return(C)
}
FtoCtemp(47)

```
No, you're not! very cold!!!